A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-15 text/formal-defnition.tex
Add a paragraph of Comparison with Hanada-Igarashi

% \AI{We should note that constants and type-level constants are not staged.}
\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}

>>>>

% \AI{We should note that constants and type-level constants are not staged.}
% \paragraph{Remark:}  \AI{

% Comparison with Hanada--Igarashi

As the end of this subsection, we compare \LMD and \LTP.
Terms of \LMD is the same with \LTP except constants.
The difference between \LMD and \LTP is their types and kinds.
First, \LMD contains $\Pi$ type instead of function type in \LTP.
Second, there two kinds of $\F$ in \LTP in order to disscuss on program residualization
although \LMD contains only one $\F$ type.
Third, \LMD contains kinding and type equivalence rules to handle dependent types.
